\cvsection{Projects}

\begin{cventries}
	\cventry
	{} % Empty position
	{Medical Records Clustering for Zhejiang Health Insurance Payment Reform} % Project
	{Zhejiang University} % Empty location
	{May. 2022 - Jun. 2023} % Empty date
	{
		\quad The objective of the project is to cluster similar medical records based on the complete annual diagnosis records in Zhejiang Province and regulate doctors' diagnostic behavior by paying the same price for each type of similar medical record through medical insurance, avoiding unnecessary excessive medical behavior. \newline
		\quad From an algorithmic perspective, the essence of the project is a large-scale clustering algorithm based on real-world data. It encompasses various stages such as data cleaning, the FP-growth frequent pattern mining algorithm, the minibatch Kmeans clustering algorithm, distributed computing, and the utilization of a Slurm cluster. I am primarily responsible for developing the code components of the project, excluding tasks related to resource scheduling and cluster construction. \newline
		The main highlights of the project include: \newline
		\vspace{4mm}
		\begin{cvitems} % Description(s) bullet points
			\item{Leveraging the unique characteristics of the data to classify it based on disease types, thereby significantly reducing the amount of data processed in a single time and enabling efficient clustering.}
			\item{In the training phase, a simple cache calculation result technology is used, which greatly reduces the time for debugging the algorithm and makes it possible to try different ideas and technical details.}
			\item{Transforming the process of traversing the FP-tree in the prediction stage into a matrix multiplication-based similarity problem. This optimization makes the code memory friendly and enables acceleration through the utilization of matrix operation libraries.}
			\item {Through the combined effects of the second and third highlights, the algorithm's iteration cycle for training and forecasting has been dramatically reduced. Previously, the process necessitated the utilization of five machines running continuously for 30 days to handle merely one-fifth of the city's data. However, with the advancements made, the same task can now be completed using only one machine within approximately three days, encompassing the entirety of the city's dataset. This improvement yields a speedup of approximately 250 times.}
		\end{cvitems}
		\vspace{2mm}
	}

	\cventry
	{} % Empty position
	{Cervical Lesion Cell Detection} % Project
	{Zhejiang University} % Empty location
	{Oct. 2020 - Mar. 2022} % Empty date
	{
		\quad The automatic detection of cervical lesion cells or cell clumps in cervical cytology images plays a crucial role in facilitating efficient cervical cancer screening. Nevertheless, accurately recognizing lesion cells faces challenges due to significant variations in appearance between single cells and cell clumps of the same lesion type and the visual similarity problem among specific abnormal cells, particularly those in adjacent differentiated stages. \newline
		My main contributions are as follows: \newline
		\vspace{4mm}
		\begin{cvitems} % Description(s) bullet points
			\item{Proposed a novel framework for cervical lesion cell detection that involves task decomposition and cell comparison.}
			\item{Decomposed the original detection task into two detection subtasks, which encouraged the network to focus on specific cell structures.}
			\item{Proposed the cell comparison utilizing normal cells as references to compare various types of abnormal cells.}
			\item{By adopting this framework, the model can learn more effective and informative lesion cell features.}
		\end{cvitems}
		\vspace{2mm}
	}

	\cventry
	{} % Empty position
	{The 12$^\text{th}$ World Robotics Sailing Championship (WRSC), 1$^\text{st}$ place} % Project
	{Zhejiang University} % Empty location
	{Oct. 2018 - Aug. 2019} % Empty date
	{
		\quad The goal is to design an autonomous sailing robot that can complete the specified tasks. I'm the leader of the software team, and responsible for the development of the decision system and vision system. Our code is avilible at \href{https://github.com/ZMART-Sailing/sailing_robot}{\textcolor{link}{[here]}}.\newline
		My main contributions are as follows: \newline
		\vspace{4mm}
		\begin{cvitems} % Description(s) bullet points
			\item{Developed a rule-based decision system with a path planning module and an obstacle avoidance module. It outputs the desired rudder angle and sail angle of the boat based on the position information and the wind information.}
			\item{Developed a vision system with obstacle detection and QR-code scanning modules deployed on Nvidia Jetson Nano.}
		\end{cvitems}
		\vspace{2mm}
	}

	\cventry
	{} % Empty position
	{Contributions to Open Source Projects} % Project
	{} % Empty location
	{} % Empty date
	{
		\begin{cvitems} % Description(s) bullet points
			% I have the ability to dig into the source code of a large project.
			\item{I have the skill to explore and analyze the source code of large projects. For examples, I contributed to \href{https://github.com/Lightning-AI/lightning}{\textcolor{link}{Pytorch-lightning}}, mmrepos including \href{https://github.com/open-mmlab/mmdetection}{\textcolor{link}{mmdetection}}, \href{https://github.com/open-mmlab/mmengine}{\textcolor{link}{mmengine}} and \href{https://github.com/open-mmlab/mmcv}{\textcolor{link}{mmcv}}, and so on.}
			\item{I have developed a boilerplate project called \href{https://github.com/shenmishajing/project_template}{\textcolor{link}{project\_template}}, which is built on PyTorch Lightning. This project incorporates a wide range of common engineering features, such as config file inheritance, cross-validation, hyperparameter tuning via wandb, and all other features provided by PyTorch Lightning. By utilizing this project, we can concentrate on model implementation without being burdened by the intricacies of engineering details.}
			% Some examples: \href{https://github.com/shenmishajing/mmdet_lightning}{\textcolor{link}{mmdet\_lightning}}, \href{https://github.com/shenmishajing/mmpretrain_lightning}{\textcolor{link}{mmpretrain\_lightning}} and \href{https://github.com/shenmishajing/detectron2_lightning}{\textcolor{link}{detectron2\_lightning}}.
			\item{Other repos include a \href{https://github.com/shenmishajing/pytorch_extension_example}{\textcolor{link}{tutorial}} and template project of cuda, a \href{https://github.com/wuzehua/Compiler}{\textcolor{link}{compiler}} based on LLVM that supports a subset syntax of the C language, a \href{https://github.com/shenmishajing/minisql}{\textcolor{link}{databest}} supported the sql language, an \href{https://github.com/wuzehua/MiniTikTok}{\textcolor{link}{andorid application}} like TikTok, and so on.}
		\end{cvitems}
	}
\end{cventries}
