\cvsection{Publications \large \href{https://scholar.google.com/citations?user=dR1J_4EAAAAJ&hl=zh-CN}{\textcolor{link}{[Google Scholar]}}}

\begin{cventries}

    \cventry
    {} % Empty position
    {\ } % Title
    {\ } % Empty location
    {} % Empty date
    {
        \vspace{-8mm}
        \begin{cvitemize2}
            \item Tingting Chen$^\dagger$, \textbf{Wenhao Zheng$^\dagger$}, Haochao Ying, Xiangyu Tan, Kexin Li, Xiaoping Li, Danny Z. Chen, Jian Wu$^*$. ``A Task Decomposing and Cell Comparing Method for Cervical Lesion Cell Detection,'' \textit{IEEE Transactions on Medical Imaging}, 2022. \href{https://ieeexplore.ieee.org/document/9744114}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Jinhong Wang$^\dagger$, Zhe Xu$^\dagger$, \textbf{Wenhao Zheng$^\dagger$}, Haochao Ying$^*$, Tingting Chen, Zuozhu Liu, Danny Z. Chen, Ke Yao$^*$, Jian Wu. ``A Transformer-based Knowledge DistillationNetwork for Cortical Cataract Grading,'' \textit{IEEE Transactions on Medical Imaging}, 2023. \href{https://ieeexplore.ieee.org/abstract/document/10294274}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item \textbf{Wenhao Zheng}, Jintai Chen, Kai Zhang, Jiahuan Yan, Jinhong Wang, Yi Cheng, Bang Du, Danny Z. Chen, Honghao Gao$^*$, Jian Wu, Hongxia Xu$^*$. ``Polygonal Approximation Learning for Convex Object Segmentation in Biomedical Images with Bounding Box Supervision,'' \textit{IEEE Journal of Biomedical and Health Informatics}, 2023, accepted. \href{https://github.com/shenmishajing/PAL}{\textcolor{link}{[Code]}}
            \vspace{1mm}
            \item Tingting Chen, \textbf{Wenhao Zheng}, Heping Hu, Chunhua Luo, Jintai Chen, Chunnv Yuan, Weiguo Lu, Danny Z. Chen, Honghao Gao$^*$ and Jian Wu$^*$. ``A Corresponding Region Fusion Framework for Multi-modal Cervical Lesion Detection,'' \textit{IEEE/ACM Transactions on Computational Biology and Bioinformatics}, 2022. \href{https://ieeexplore.ieee.org/document/9784879}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item \textbf{Wenhao Zheng}, Qiwei Zhao, Ping Zhang, Hongxia Xu, Huaxiu Yao$^*$. ``$M^3$OE: Multi-Modal Mix of Experts Clinical Trial Outcome Prediction with Unified Transformer Encoders,'' \textit{ACL Rolling Review}, 2023, under review.
            \vspace{1mm}
            \item Yi Cheng, Haochao Ying$^*$, Renjun Hu, Jinhong Wang, \textbf{Wenhao Zheng}, Xiao Zhang, Danny Z. Chen, Jian Wu. ``Robust Image Ordinal Regression with Controllable Image Generation,'' \textit{International Joint Conference on Artificial Intelligence}, 2023. \href{https://arxiv.org/abs/2305.04213}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Jinhong Wang$^\dagger$, Jing, Danny Z. Chenwen Wang$^\dagger$, Tingting Chen, \textbf{Wenhao Zheng}, Zhe Xu, Xingdi Wu, Wen Xu$^*$, Haochao Ying$^*$, Danny Z. Chen, and Jian Wu. ``CTT-Net: A Multi-view Cross-token Transformer for Cataract Postoperative Visual Acuity Prediction,'' \textit{IEEE International Conference on Bioinformatics and Biomedicine}, 2022. \href{https://ieeexplore.ieee.org/document/9995392}{\textcolor{link}{[Link]}}
            \vspace{1mm}
            \item Tingting Chen$^\dagger$, Yi Cheng$^\dagger$, Jinhong Wang, Zhaoxia Yang, \textbf{Wenhao Zheng}, Danny Z. Chen, and Jian Wu$^*$. ``Automating Blastocyst Formation and Quality Prediction in Time-Lapse Imaging with Adaptive Key Frame Selection,'' \textit{Medical Image Computing and Computer Assisted Intervention}, 2022. \href{https://link.springer.com/chapter/10.1007/978-3-031-16440-8_43}{\textcolor{link}{[Link]}}
        \end{cvitemize2}
    }
\end{cventries}
