\cvsection{Research Projects}

\begin{cventries}

	\cventry
	{} % Empty position
	{Research on Cervical Lesion Cell Detection} % Project
	{Hangzhou} % Empty location
	{Oct. 2020 - Mar. 2022} % Empty date
	{
		Automatic detection of cervical lesion cells or cell clumps using cervical cytology images is critical for efﬁcient cervical cancer screening. I have studied this project through three aspects: \newline
		\vspace{4.5mm}
		\begin{cvitems} % Description(s) bullet points
			\item{The large appearance variances between single cell and cell clumps of the same lesion type pose difﬁculties for accurate lesion cell recognition.}
			\item{Normal cells can be a good reference for abnormal cell recognition.}
			\item{The visual similarity problem among certain abnormal cells, especially those in adjacent differentiated stages.}
		\end{cvitems}
		\vspace{4.5mm}
		For the above issues, I have studied a novel task decomposing and cell comparing framework for cervical lesion cell detection. The task decomposing scheme decomposes the original detection task into two detection subtasks, which encourages the network to focus on specific cell structures. The cell comparing scheme imitates clinicians to utilize normal cells as references and compare different types of abnormal cells, and it allows the model to learn more effective and useful lesion cell features.
	}

	\cventry
	{} % Empty position
	{Research on Zhejiang Health Insurance Payment Reform} % Project
	{Hangzhou} % Empty location
	{May. 2022 - Jun. 2023} % Empty date
	{
		The objective of the project is to cluster similar medical records based on the complete annual diagnosis records in Zhejiang Province and regulate doctors' diagnostic behavior by paying the same price for each type of similar medical record through medical insurance, avoiding unnecessary excessive medical behavior. \newline
		From an algorithmic perspective, the essence of the project is a large-scale clustering algorithm based on real-world data. It encompasses various stages such as data cleaning, the FP-growth frequent pattern mining algorithm, the minibatch Kmeans clustering algorithm, distributed computing, and the utilization of a Slurm cluster. I am primarily responsible for developing the code components of the project, excluding tasks related to resource scheduling and cluster construction. \newline
		The main highlights of the project include: \newline
		\vspace{3.5mm}
		\begin{cvitems} % Description(s) bullet points
			\item{Leveraging the unique characteristics of the data to classify it based on disease types, thereby significantly reducing the amount of data processed in a single time and enabling efficient clustering.}
			\item{In the training phase, a simple cache calculation result technology is used, which greatly reduces the time for debugging the algorithm and makes it possible to try different ideas and technical details.}
			\item{Transforming the process of traversing the FP-tree in the prediction stage into a matrix multiplication-based similarity problem. This optimization makes the code memory friendly and enables acceleration through the utilization of matrix operation libraries.}
			\item {Through the combined effects of the second and third highlights, the algorithm's iteration cycle for training and forecasting has been dramatically reduced. Previously, the process necessitated the utilization of five machines running continuously for 30 days to handle merely one-fifth of the city's data. However, with the advancements made, the same task can now be completed using only one machine within approximately three days, encompassing the entirety of the city's dataset. This improvement yields a speedup of approximately 250 times.}
		\end{cvitems}
	}

\end{cventries}
